
<!--- QUICK METHOD TO INSERT REPEATED CHUNKS --->
```{r repeat-chunks,eval=F}
library(tidyverse)
library(knitr)

# Get the numeric variables from mtcars for plotting
mtcars_numeric <- mtcars %>%
  select_if(is.numeric)

# Get the variable names
var_names <- names(mtcars_numeric)

# Create a list to store our expanded chunks
src <- lapply(seq_along(var_names), function(i) {
  # Get the current variable name
  var_name <- var_names[i]
  
  # Create a label and caption
  label <- paste0('mtcars-var-', i)
  caption <- paste('Distribution of', var_name)
  
  # Create the R chunk to write
  r_chunks_to_write <- c(
    "```{r}",
    "#| label: {{label}}",
    "#| fig-height: 5",
    "#| fig-width: 6",
    "#| fig-cap: '{{cap}}'",
    "mtcars %>%",
    "  mutate(sqrt_{{var_name}} = sqrt({{var_name}}),",
    "         log_{{var_name}} = log({{var_name}} + 0.1)) %>%",  # Adding 0.1 to avoid log(0)
    "  pivot_longer(cols = c({{var_name}}, sqrt_{{var_name}}, log_{{var_name}}),",
    "               names_to = 'Transform', values_to = 'Value') %>%",
    "  ggplot(aes(x = Value)) +",
    "  geom_histogram(bins = 15, fill = 'steelblue', color = 'black') +",
    "  facet_wrap(~ Transform, scales = 'free') +",
    "  theme_minimal() +",
    "  labs(title = 'Distribution of {{var_name}} with different transformations')",
    "```\n\n"
  )
  
  # Use knit_expand to substitute our variables
  knit_expand(text = r_chunks_to_write,
              label = label,
              cap = caption,
              var_name = var_name)
})

# Output the source to a file
sink('repeat_chunks.qmd')
for (i in seq_along(src)) {
  cat(src[[i]])
}
sink()

# Preview what will be written to the file
cat("The first chunk that will be written to mtcars_plots.qmd:\n\n")
cat(src[[1]])
# Now the qmd file can be edited to have comments added
# The contents of the qmd file are included in your report using the child option (example)
# there are saved in strings for easy and reproducible compilation
```

```{r chunk-insert, child='repeat_chunks.qmd',eval=T}

```
